%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Simple LaTeX Resume by Biswajit Paria %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm, algorithmicx}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{url}
\usepackage{parskip}
\usepackage[a4paper, total={7in,10in}]{geometry}

\pagenumbering{gobble}

\setlength{\parindent}{0pt}
\setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
\renewcommand{\baselinestretch}{1}

\newcommand{\heading}[1]{
 {\large \textbf{#1}}
  \vspace{0.4em}
  \hrule
  \vspace{0.4em}
}

\newcommand{\EntryGap}{\vspace{0.5cm}}
\newcommand{\SmallEntryGap}{\vspace{0.2cm}}
\newcommand{\mdot}{$\ \ \cdot\ \ $}

\newcommand{\indentedpar}[1]{
  \hangindent=1cm \hangafter=0 #1
}

\newenvironment{compactitemize}
{ \begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{ \end{itemize}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\Large \textbf{Biswajit Paria}}\\
5th year undergraduate (dual degree) \hfill biswajitsc@iitkgp.ac.in\\
Dept. of Computer Science and Engineering \hfill biswajitsc@gmail.com\\
Indian Institute of Technology Kharagpur \hfill  +91-8348949676  
\EntryGap


%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\heading{Education}
\SmallEntryGap
\textbf{Indian Institute of Technology Kharagpur, India} \hfill Jul 2012 - Apr 2017\\
Bachelor and Master of Technology (dual degree) with Honours\\
in Computer Science and Engineering\\
GPA 9.77/10.0, highest among final year dual degree students.

\SmallEntryGap
\textbf{Kendriya Vidyalaya IIT Kharagpur} \hfill Jul 2010 - Apr 2012\\
All India Senior School Certificate Examination (AISSCE)\\
Central Board of Secondary Education (CBSE)\\
Percentage score 92.4\%

\SmallEntryGap
\textbf{Kendriya Vidyalaya IIT Kharagpur} \hfill Apr 2005 - Apr 2010\\
All India Secondary School Examination (AISSE)\\
Central Board of Secondary Education (CBSE)\\
GPA 9.8/10.0

\EntryGap
\heading{Interests}

\SmallEntryGap

My broad interests are Machine Learning and AI. Currently I am working
on deep learning, particularly on vision tasks and generative modelling.
In AI, I am mostly interested in  Reinforcement Learning including Deep Reinforcement
Learning and algorithmic topics such as online learning and its bounds.

\EntryGap

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTERNSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\heading{Internships}

\textbf{Indian Institute of Science, Bangalore, India} \hfill Summer 2016\\
\textbf{Natural Language Inference (NLI) using Deep Learning for NLP}\\
under Prof. Ambedkar Dukkipati

\SmallEntryGap

\indentedpar{
  Worked with the Stanford NLI dataset. Given two sentences, the task
  is to determine whether the sentences are related as an entailment, contradiction
  or are neutral. We explored models using LSTMs, Attention
  Models, and Dependency Parses. Eventually, we came up with an hybrid model which
  is currently under preparation for submission in a reputed conference.
}

\SmallEntryGap

\textbf{University of Southern California, Los Angeles, USA} \hfill Summer 2015\\
\textbf{Computational Phenotyping using Deep Neural Networks}\\
under Prof. Yan Liu

\SmallEntryGap

\indentedpar{
  Worked with ICU time series data consisting of a multitude of medical parameters
  and used deep learning with a laplacian prior regularizer, to predict health outcomes. We
  performed causality analysis on the final layer nodes, analyzed the activations of 
  the most \emph{causal} nodes using decision trees, and extracted their maximally activating 
  inputs. This analysis is a step towards developing a robust automated symptom analyzer.
}

\SmallEntryGap
\textbf{Indian Institute of Technology Kharagpur, India} \hfill Summer 2014\\
\textbf{On Farey Table and its Compression for Space Optimization with Guaranteed Error Bounds}\\
under Prof. Partha Bhowmick

\SmallEntryGap

\indentedpar{
  Studied the number theoretic properties of Farey Sequences and the
  Farey Table, and came up with a novel algorithm for a lossy compression of the 
  Farey Table. The Farey Table is an useful data-structure in digital geometry.
  It's quadratic size ($\Theta(n^2)$) prohibits its use for large dimensions. The
  compressed table has a size of ($O(n\log n)$), thus allowing table creation for
  large $n$.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\EntryGap
\heading{Research Projects}
\SmallEntryGap

\textbf{Bachelor's Thesis} \hfill 2015 - 2016\\
\textbf{Visualization Regularizers for Neural Network based Image Recognition}\\
Advisor: Prof. Pabitra Mitra

\SmallEntryGap

\indentedpar{
    Introduced a novel regularizer for Neural Networks
    based on the \emph{visualizations} of the hidden nodes. 
    We leveraged the closed algebraic form of the
    visualizations of the first layer nodes, and used it as a smoothness prior.
    We show that the regularizer is a special case of the 
    general Tikhonov regularization. Experimental results show that the 
    visualization regularizers are an improvement over standard L2 regularizers.
}

\SmallEntryGap

\textbf{Advanced Machine Learning Course Project} \hfill Spring 2016 \\
\textbf{Data Matrix Size Reduction using Sampling for Scalable Machine Learning}\\
under Prof. Sourangshu Bhattacharya, IIT Kharagpur and Prof. Anirban Dasgupta, IIT Gandhinagar

\SmallEntryGap

\indentedpar{
  Implemented various sampling and projection algorithms on synthetically generated
  datasets and tested on binary SVM classification. We implemented Clarkson Woodruff's
  feature sampling, Achlioptas' methods for euclidian distance preservations and 
  low rank approximations, and leverage score based sampling.
}


%%%%%%%%%%%%%%%%%%%%%%%%%% Papers %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EntryGap

\heading{Papers}
  \SmallEntryGap
  Avisek Lahiri, Biswajit Paria, Prabir Kumar Biswas. 
  \textbf{Forward Stagewise Additive Model for Collaborative Multiview Boosting.}
  \emph{IEEE Transactions in Neural Networks and Learning Systems}, 2016.
  (Under minor revision)
  
  \SmallEntryGap
  Biswajit Paria, Anirban Santara, Pabitra Mitra.
  \textbf{Visualization Regularizers for Neural Network based Image Recognition.}
  \emph{arXiv preprint arXiv:}, 2016
  
  \SmallEntryGap
  Sandipan Sikdar, Marcin Bodych, Rajib Ranjan Maiti, Biswajit Paria, 
  Niloy Ganguly, Tyll Krueger, Animesh Mukherjee.
  \textbf{On the broadcast of segmented messages in dynamic networks}.
  \emph{IEEE INFOCOM Workshops}, 2015.


%%%%%%%%%%%%%%%%%%%%%%%%%% OTHER PROJECTS     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\EntryGap

\heading{Other Projects}
  \SmallEntryGap
  
  \textbf{Distributed P2P File Sharing and Search System}, Distributed Systems Course Project \hfill Spring 2016\\
  Implemented a P2P file sharing platform for distributed search and download,\\
  with replication of the file database.
  \SmallEntryGap
  
  \textbf{A Search Engine for Mathematical Formulae}, NLP Course Project \hfill Autumn 2015\\
  To search for text and mathematical formulae in academic articles.
  \SmallEntryGap
  
  \textbf{TinyC Compiler}, Compilers Course Project \hfill Autumn 2014\\
  A compiler for a C-like language.
  \SmallEntryGap
  
  \textbf{Genetic Algorithm based Jigsaw Solver} \hfill Jan - 2014\\
  A jigsaw puzzle solver for images divided into uniform sized squares and randomly shuffled.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ACADEMIC HONORS & AWARDS %%%%%%%%%%%%%%%%%%%%%%


\EntryGap
\heading{Academic Honors and Awards}
 \SmallEntryGap
 
 \textbf{Goralal Syngal Scholarship} \hfill 2015 \& 2016\\
 for academic excellence at IIT Kharagpur.
 \SmallEntryGap
 
 \textbf{Charubala Devi Memorial Prize} \hfill 2015\\
  for being the best in order of merit among all third year students.
  \SmallEntryGap
  
 \textbf{Viterbi-India Scholarhip} \hfill 2015\\
  for funding a summer internship at USC. One of the 20 scholars in India.
  \SmallEntryGap
  
 \textbf{ACM ICPC 2015 and 2016 World Finalist} \hfill 2015\\
  Our team qualified for the International Collegiate Programming Competition (ICPC)\\
  twice, in 2015 and 2016. One of the 7 teams from India.
  \SmallEntryGap
  
 \textbf{JBNSTS third best project} \hfill 2014\\
  Awarded for our work on Counting Dyck Paths of Bounded Height.
  \SmallEntryGap
  
 \textbf{Jagadish Bose National Science Talent Search (JBNSTS) Scholar} \hfill 2013\\
  Awarded to 30 candidates in the state of West Bengal.
  \SmallEntryGap
  
 \textbf{Indian National Physics Olympiad (INPhO) Awardee} \hfill 2012\\
  Among top 30 candidates in India.\\
  Selected to attend the 
  International Physics Olympiad (IPhO) selection camp.
  \SmallEntryGap
  
 \textbf{Kishore Vaigyanik Protsahan Yojana (KVPY) Scholar} \hfill 2011\\
  by Dept. of Science and Technology, Govt. of India for exceptional aptitude in basic sciences.\\
  Stood 7th in India.
  \SmallEntryGap
  
 \textbf{Indian National Mathematical Olympiad (INMO) Awardee} \hfill 2010\\
  Among top 30 candidates in India.\\
  Selected to attend the International Mathematical Olympiad Training Camp (IMOTC).
  \SmallEntryGap
  
 \textbf{Australian Mathematics Competition (AMC) Gold Medallist}\hfill 2009\\
  Recieved a Gold Medal in the Intermediate Division. One of the 23 medallists in the world.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SKILLS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\EntryGap
\heading{Technical Skills}
\SmallEntryGap
\textbf{Proficient in} C, C++, Python, Java, Bash, Matlab, Tensorflow, Numpy\\
\textbf{Familiar with} Mathematica, HTML, Javascript, Caffe, Theano, Scikit-learn,\\
Keras, Lasagne, Nltk, Stanford Core-NLP



%%%%%%%%%%%%%%%%%%%%%%%%%% RELEVANT COURSES   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\EntryGap
\heading{Coursework}
\SmallEntryGap
\textbf{Relevant}\\
Machine Learning \mdot Advanced Machine Learning \mdot Probability and Statistics \mdot Speech and Natural Language Processing 
\mdot Artificial Intelligence \mdot Matrix Algebra \mdot Information Retrieval

\SmallEntryGap
\textbf{Others}\\
Algorithms-I \& II \mdot Discrete Mathematics \mdot Parallel and Distributed Algorithms 
\mdot Selected Topics in Algorithms  \mdot Computational Statistics
\mdot Advanced Graph Theory \mdot Database Management Systems \mdot Operating Systems
\mdot Computer Networks \mdot Computer Organization and Architecture \mdot Theory of Computation
\mdot Operations Research \mdot High Performance Computer Architecture \mdot Distributed Systems
\mdot Cryptography

\EntryGap
\heading{Extra Curricular Activities}
\SmallEntryGap
Machine Learning Teaching Assistant \hfill Autumn 2016\\
Responsibilities include interaction with students, and supervising and
and evaluating term projects.

\SmallEntryGap
Machine Learning Reading Group\hfill 2016\\
Organizer and speaker at the weekly machine learning reading group.

\SmallEntryGap
National Service Scheme \hfill 2012-2014\\
Helped under-privileged children in academics and created an enjoyable school 
atmosphere for learning.


\end{document}
